---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "##",
    dpi = 250,
    fig.path = "man/images/"
)
```

# irishbabynames

```{r, include=FALSE}
library(irishbabynames)
```


## Description

The irishbabynames package provides tools and interactive visualizations to explore baby name trends in Ireland throught the years 1964 to 2024, gathered from the [Central Statistics Office](https://www.cso.ie/en/interactivezone/visualisationtools/babynamesofireland/).

The package contains the dataset `irishbabynames` with `r  format(nrow(irishbabynames), big.mark = ",")` observations on variables: `year(1964-2024)`, `gender`, `Name`, `Statistic`. Due to confidentiality reasons, only names with 3 or more instances in the relevant year are included.

The package 4 visualisations that can be used to explore patterns of baby names in Ireland over time:


* `plot_trend`: The trend of a name throughout the years(1964-2024) .


* `plot_similar_girlsnames`: Phonetically similar names in girls throughout the 
years(1964-2024)


* `plot_similar_boysnames`: Phonetically similar names in boys throughout the years(1964-2024)


* `plot_unisex_names`: Unisex names starting with a specific letter in a given year.


It is inspired by Hadley Wickham's [**babynames**](https://cran.r-project.org/package=babynames) package.

## Installation

The package is hosted on GitHub and not available at CRAN. To install the latest development version:

```{r eval = FALSE}
if (!require("remotes")) {
    install.packages("remotes")
}
remotes::install_github("SuryenduManoj/irishbabynames")
```

