---
title: "Irish Baby Names"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{irishbabynames}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(irishbabynames)
data("irishbabynames")
```


## Introduction

The irishbabynames package provides tools and interactive visualizations to explore baby name trends in Ireland using data from the CSO.

This vignette demonstrates plots that shows:

  1. The trend of a name throughout the years(1964-2024)
  
  2. Similar names in girls throughout the years(1964-2024)
  
  3. Similar names in boys throughout the years(1964-2024)
  
  4. Unisex names starting with a specific letter in a given year
  
  5. Launching the interactive Shiny dashboard
  
  
Note: The plots in this vignette are interactive. For full interactivity, view the vignette in an RStudio Viewer or using vignette("irishbabynames").
  
  
## Trend Plot Example

```{r eval = FALSE}
plot_trend("Aoife")
```

## Similar Names Example - for Girls

```{r eval = FALSE}
plot_similar_girlsnames("Aoife")
```

## Similar Names Example - for Boys

```{r eval = FALSE}
plot_similar_boysnames("John")
```

## Unisex Names for a particular year

```{r eval = FALSE}
plot_unisex_names("A","2024")
```

## Launch Shiny dashboard

Use this function to open an interactive dashboard for exploring Irish baby names using tabs and visualizations.

```{r eval = FALSE}
irishbabynames_dashboard()
```

