---
title: "Irish Baby Names"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{irishbabynames}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(irishbabynames)
data("irishbabynames")
```


## Introduction

The irishbabynames package provides tools and interactive visualizations to explore baby name trends in Ireland using data from the CSO.

This vignette demonstrates plots that shows:

1. The trend of a name throughout the years(1964-2024) 
2. Similar names in girls throughout the years(1964-2024)
3. Similar names in boys throughout the years(1964-2024)
4. Unisex names starting with a specific letter in a given year
5. Launching the interactive Shiny dashboard
  
  
  
## Trend Plot Example

The plot_trend() function visualizes the trend of a name across years.
```{r eval = FALSE}
plot_trend("Aoife")
```

## Similar Names Example - for Girls

The plot_similar_girlsnames() function shows girls' names with similar phonetics over the years.
```{r eval = FALSE}
plot_similar_girlsnames("Aoife")
```

## Similar Names Example - for Boys

The plot_similar_boysnames() function shows phonetically similar boys' names.
```{r eval = FALSE}
plot_similar_boysnames("John")
```

## Unisex Names for a particular year

Use the plot_unisex_names() function to display unisex names starting with a particular letter in a given year.
```{r eval = FALSE}
plot_unisex_names("A","2024")
```

## Launch Shiny dashboard

Use this function to open an interactive dashboard for exploring Irish baby names using tabs and visualizations.
```{r eval = FALSE}
irishbabynames_dashboard()
```

